Simulation Study: Varying Null Proportion

### 2018-04-20 datasets/simulations/simulations-informative-cubic.Rmd
Update sim params w/ larger signal

For comparison, we also include the ASH q-values.

```{r}
bd <- addBMethod(bd, "ashq", ashr::ash, ashr::get_qvalue,
                 betahat = effect_size, sebetahat = SE)
```

@@

```{r gauss-parameters}
tstat <- rnorm_generator(3)       # functional: dist of alternative test stats
tstat_dist <- rnorm_perturber(1)  # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1)    # functional: dist to calc p-values
seed <- 608
```

@@

```{r chisq4-parameters}
tstat <- rnorm_generator(12)       # functional: dist of alternative test stats
tstat_dist <- rchisq_perturber(4)  # functional: sampling dist/noise for test stats
null_dist <- rchisq_pvaluer(4)     # functional: dist to calc p-values
seed <- 1023
```

>>>>

@@

```{r gauss-parameters}
tstat <- rnorm_generator(4)       # functional: dist of alternative test stats
tstat_dist <- rnorm_perturber(1)  # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1)    # functional: dist to calc p-values
seed <- 608
```

@@

```{r chisq4-parameters}
tstat <- rnorm_generator(15)       # functional: dist of alternative test stats
tstat_dist <- rchisq_perturber(4)  # functional: sampling dist/noise for test stats
null_dist <- rchisq_pvaluer(4)     # functional: dist to calc p-values
seed <- 1023
```

### 2018-04-20 datasets/simulations/simulations-varyingeffectsize.Rmd
Update sim params w/ larger signal

```{r parameters-shared}
m <- 20000                        # integer: number of hypothesis tests
pi0 <- pi0_sine(0.90)             # numeric: proportion of null hypotheses
tstat_dist <- rnorm_perturber(1)  # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1)    # functional: dist to calc p-values
icovariate <- runif               # functional: independent covariate
```

>>>>

```{r parameters-shared}
m <- 20000                          # integer: number of hypothesis tests
pi0 <- pi0_sine(0.90)               # numeric: proportion of null hypotheses
tstat_dist <- rnorm_perturber(1/2)  # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1/2)    # functional: dist to calc p-values
icovariate <- runif                 # functional: independent covariate
```

### 2018-04-20 datasets/simulations/simulations-varyingpi0.Rmd
Update sim params w/ larger signal

```{r parameters-shared}
m <- 20000                        # integer: number of hypothesis tests
tstat <- rnorm_generator(3)       # functional: dist of alternative test stats
tstat_dist <- rnorm_perturber(1)  # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1)    # functional: dist to calc p-values
icovariate <- runif               # functional: independent covariate
```

>>>>

```{r parameters-shared}
m <- 20000                        # integer: number of hypothesis tests
tstat <- rnorm_generator(4)       # functional: dist of alternative test stats
tstat_dist <- rnorm_perturber(1)  # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1)    # functional: dist to calc p-values
icovariate <- runif               # functional: independent covariate
```
